% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.

\IEEEPARstart{T}{he} human face is one of the most popular
characteristic which can be used in the biometric security system
to identify or verify a user. Face is an acceptable biometric
modality because it can be captured from a distance, even
without physical contact of the user being identified. Thus the
identification or verification does not require cooperation of the
user. Recognition systems based on human face are used for a
wide variety of applications, due to these benefits.\cite{Eurocon}
The recognition of the faces in different contexts
enables various applications such as surveillance monitoring,
social networking, and human-computer interaction.\cite{Forensics}


For example, in the recent event of Boston marathon bombings,
images of the suspects taken from street surveillance cameras
aided the FBI to identify the suspects.
<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<06905824>


Face recognition includes the studies of automatically
identifying or verifying a person from an image or video
sequences. Face identification refers to determining the ID of
the person, given as a probe, from a large pool of candidates
in the gallery. Face verification or face authentication is the problem of deciding whether a given pair of images are
of the same person or not\cite{Forensics}.

