We validated our implementations with our database. It contains around 15 training and 200 testing pictures of each team member. The test set contains one more person (Andris) to test the result for an unknown face.

The average successful classification ratio.
\begin{itemize}
	\item Eigen face: 71.65\%
	\item Fisher face: 90.80\%
	\item LBPH: 86.81\%
\end{itemize}

The results for the combined classifier:
\begin{table}[h]
	\begin{tabular}{l|l}
		** Classification Rate:                ** &          \\ \hline
		Adrian                                    & 94.26\%  \\
		Axel                                      & 94.12\%  \\
		Carole                                    & 99.63\%  \\
		Domi                                      & 99.39\%  \\
		Gareth                                    & 100.00\% \\ \hline
		Full Result                               & 97.48\%  \\ 
		\\
		** Unsuccesful classification:         ** &          \\ \hline
		Adrian:                                   & 13.64\%  \\
		Axel:                                     & 36.57\%  \\
		Carole:                                   & 5.61\%   \\
		Domi:                                     & 25.23\%  \\
		Gareth:                                   & 0.69\%  \\ \hline
		Andris:                                   & 73.10\%  
	\end{tabular}
	\label{CombinedResult}
	\title{Combined classifier validation result}
\end{table}

The results show that the combined classifier has a 7\% better rate of recognition than the Fisherfaces method. The reason is the usage of the boosting. We combined 3 independent method to achieve a better solution than any of it. Another important difference is that the Fisher and the Eigenface method did not use thresholding for the decision. Because of that if an attempt was made to classify an unknown face, the method would return one of the known labels in any circumstances. The combined classifier result shows that the unknown person (Andris) 73\% classified as non-recognisable face.

As we mentioned in the \ref{Implementation:preprocessing} chapter we applied preprocessing to the pictures before the training and testing. To validate the previous assumption that this method improves the algorithm a lot, we tested the combined classifier for the same dataset without preprocessing.

\begin{table}[h]
	\begin{tabular}{ll}
		\multicolumn{1}{l|}{** Classification Rate:                **} &         \\ \hline
		\multicolumn{1}{l|}{Adrian}                                    & 54.96\% \\
		\multicolumn{1}{l|}{Axel}                                      & 71.43\% \\
		\multicolumn{1}{l|}{Carole}                                    & 96.48\% \\
		\multicolumn{1}{l|}{Domi}                                      & 59.89\% \\
		\multicolumn{1}{l|}{Gareth}                                    & 88.41\% \\
		\multicolumn{1}{l|}{Full Result}                               & 74.23\% \\
		&         \\
		\multicolumn{1}{l|}{** Unsuccesful classification:         **} &         \\ \hline
		\multicolumn{1}{l|}{Adrian:}                                   & 8.26\%  \\
		\multicolumn{1}{l|}{Axel:}                                     & 16.42\% \\
		\multicolumn{1}{l|}{Carole:}                                   & 10.18\% \\
		\multicolumn{1}{l|}{Domi:}                                     & 14.22\% \\
		\multicolumn{1}{l|}{Gareth:}                                   & 4.17\%  \\ \hline
		\multicolumn{1}{l|}{Andris}                                    & 53.22\%
	\end{tabular}
\end{table}

 The table shows that without preprocessing the recognition rate decreased 23\% while the unknown face (Andris) had an unsuccessful recognition rate decrease by 20\%. We can say that the normalisation process for the images which have a 5-10\% margin around the face makes a serious improvement.